Integrating Common Ground and Informativeness in Pragmatic Word Learning

### 2019-04-26 papers/cogsci2019/cogsci2019.Rmd
first draft paper si

author-information: > 
   \author{{\large \bf Manuel Bohn} \\ \texttt{bohn@stanford.edu} \\ Psychology, Stanford University \\ LFE, Leipzig University 
    \And {\large \bf Michael Henry Tessler} \\ \texttt{tessler@mit.edu} \\ Department of Brain and Cognitive Sciences \\ Massachusetts Institute of Technology
    \And {\large \bf Michael C. Frank} \\ \texttt{mcfrank@stanford.edu} \\ Department of Psychology \\ Stanford University}

@@

A range probabilistic frameworks been used to model word learning [e.g. @fazly2010probabilistic; @frank2009using; @xu2007word]. RSA models differ from other approaches in that they treat word learning as the outcome of a social reasoning process. In contrast to models for cross-situational word learning [@fazly2010probabilistic; @frank2009using], RSA models show how learning might occur in a one shot scenario based on pragmatic reasoning alone. While the ad hoc informativeness inference characteristic for RSA would be predicted by the model of Xu and Tenenbaum [-@xu2007word], in their work it follows from the "size principle" of generalization [@tenenbaum2001generalization] and not from social reasoning. In cotrast to RSA, this approach does not offer a straightforward way to incorporate other types of social information such as expectations following from common ground.

@@

MB received funding from the European Union’s Horizon 2020 research and innovation programme under the Marie Sklodowska-Curie grant agreement No 749229.

>>>>

author-information: > 
   \author{{\large \bf Manuel Bohn} \\ \texttt{bohn@stanford.edu} \\ Department of Psychology \\ Stanford University\\ LFE \\Leipzig University 
    \And {\large \bf Michael Henry Tessler} \\ \texttt{tessler@mit.edu} \\ Department of Brain and Cognitive Sciences \\ Massachusetts Institute of Technology
    \And {\large \bf Michael C. Frank} \\ \texttt{mcfrank@stanford.edu} \\ Department of Psychology \\ Stanford University}

@@

A range of probabilistic models have been used to model word learning [e.g. @fazly2010probabilistic; @frank2009using; @xu2007word]. RSA models differ from these approaches in that they treat word learning as the outcome of a social reasoning process. In contrast to models for cross-situational word learning [@fazly2010probabilistic; @frank2009using], RSA models show how learning might occur in a one shot scenario based on pragmatic reasoning alone. While the ad-hoc informativeness inference characteristic for RSA would be predicted by the model of Xu and Tenenbaum [-@xu2007word], in their work it follows from the "size principle" of generalization [@tenenbaum2001generalization] and not from social reasoning. In contrast to RSA, this approach does not offer a straightforward way to incorporate other types of social information such as expectations following from common ground.

@@

MB received funding from the European Union’s Horizon 2020 research and innovation programme under the Marie Sklodowska-Curie grant agreement No 749229. MCF was supported by a Jacobs Foundation Advanced Research Fellowship and NSF #1456077.

### 2019-04-26 papers/cogsci2019/cogsci2019.tex
first draft paper si

\author{{\large \bf Manuel Bohn} \\ \texttt{bohn@stanford.edu} \\ Psychology, Stanford University \\ LFE, Leipzig University 
 \And {\large \bf Michael Henry Tessler} \\ \texttt{tessler@mit.edu} \\ Department of Brain and Cognitive Sciences \\ Massachusetts Institute of Technology
 \And {\large \bf Michael C. Frank} \\ \texttt{mcfrank@stanford.edu} \\ Department of Psychology \\ Stanford University}

@@

A range probabilistic frameworks been used to model word learning (e.g.
Fazly, Alishahi, \& Stevenson, 2010; Frank, Goodman, \& Tenenbaum, 2009;
Xu \& Tenenbaum, 2007). RSA models differ from other approaches in that
they treat word learning as the outcome of a social reasoning process.
In contrast to models for cross-situational word learning (Fazly et al.,
2010; Frank et al., 2009), RSA models show how learning might occur in a
one shot scenario based on pragmatic reasoning alone. While the ad hoc
informativeness inference characteristic for RSA would be predicted by
the model of Xu and Tenenbaum (2007), in their work it follows from the
``size principle'' of generalization (Tenenbaum \& Griffiths, 2001) and
not from social reasoning. In cotrast to RSA, this approach does not
offer a straightforward way to incorporate other types of social
information such as expectations following from common ground.

@@

MB received funding from the European Union's Horizon 2020 research and
innovation programme under the Marie Sklodowska-Curie grant agreement No
749229.

>>>>

\author{{\large \bf Manuel Bohn} \\ \texttt{bohn@stanford.edu} \\ Department of Psychology \\ Stanford University\\ LFE \\Leipzig University 
 \And {\large \bf Michael Henry Tessler} \\ \texttt{tessler@mit.edu} \\ Department of Brain and Cognitive Sciences \\ Massachusetts Institute of Technology
 \And {\large \bf Michael C. Frank} \\ \texttt{mcfrank@stanford.edu} \\ Department of Psychology \\ Stanford University}

@@

A range of probabilistic models have been used to model word learning
(e.g. Fazly, Alishahi, \& Stevenson, 2010; Frank, Goodman, \& Tenenbaum,
2009; Xu \& Tenenbaum, 2007). RSA models differ from these approaches in
that they treat word learning as the outcome of a social reasoning
process. In contrast to models for cross-situational word learning
(Fazly et al., 2010; Frank et al., 2009), RSA models show how learning
might occur in a one shot scenario based on pragmatic reasoning alone.
While the ad-hoc informativeness inference characteristic for RSA would
be predicted by the model of Xu and Tenenbaum (2007), in their work it
follows from the ``size principle'' of generalization (Tenenbaum \&
Griffiths, 2001) and not from social reasoning. In contrast to RSA, this
approach does not offer a straightforward way to incorporate other types
of social information such as expectations following from common ground.

@@

MB received funding from the European Union's Horizon 2020 research and
innovation programme under the Marie Sklodowska-Curie grant agreement No
749229. MCF was supported by a Jacobs Foundation Advanced Research
Fellowship and NSF \#1456077.
